Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-13 manuscript/manuscript.tex
Update delta determination

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]
    {figures/grid-search.pdf}
}{
\includegraphics[width=0.5\linewidth]
    {figures/grid-search.pdf}
}
\caption{
    Numerical error exploration in the $D$-$\delta$ space.
    The percentage difference values were obtained from the comparison between the
    analytical solution and the numerical approximation of the gravitational fields ($V$
    and $g_z$) generated by a spherical shell with an exponential density function
    (Eq.~\ref{eq:density-exp}).
    These comparisons were carried out on the ``Global'' grid (Table~\ref{tab:grids}),
    with only five spherical shell models made out of the second tesseroid collection
    from Table~\ref{tab:tess-colections} with the different thicknesses defined in the
    same Table, and density function with $b = 30$.
    The percentage difference values are obtained as the maximum difference
    corresponding to each spherical shell model.
    The points inside the dashed line are the ones that present an error lower than
    0.1\%.
    }
\label{fig:grid-search}
\end{figure}

@@

Having chosen values of $D$ equal to the linear density case, we are free to explore the
integration error as a function of $\delta$ in more detail and how it varies for
different values of $b$ (Eq.~\ref{eq:density-exp}).
We perform the error calculations for the ``Big Grid'' configuration
(Table~\ref{tab:grids}) for two spherical shell models with 1km and 35km thickness.
The calculations are repeated for different values of $b$ to examine the error variation
with the sharpness of the density function.
Because larger $\delta$ values result in fewer tesseroid divisions,
our intention is to find the highest value of $\delta$ whose numerical error is bellow
the $0.1\%$ threshold.

>>>>

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]
    {figures/grid-search.pdf}
}{
\includegraphics[width=0.5\linewidth]
    {figures/grid-search.pdf}
}
\caption{
    Numerical error exploration in the $D$-$\delta$ space.
    The percentage difference values were obtained from the comparison between the
    analytical solution and the numerical approximation of the gravitational fields ($V$
    and $g_z$) generated by a spherical shell with an exponential density function
    (Eq.~\ref{eq:density-exp}).
    These comparisons were carried out on the ``Global'' grid (Table~\ref{tab:grids}),
    with only five spherical shell models made out of the second tesseroid collection
    from Table~\ref{tab:tess-collections} with the different thicknesses defined in the
    same Table, and density function with $b = 30$.
    The percentage difference values are obtained as the maximum difference
    corresponding to each spherical shell model.
    The points inside the dashed line are the ones that present an error lower than
    0.1\%.
    The $D$ value obtained for the linear density case for each gravitational field is
    also shown.
    }
\label{fig:grid-search}
\end{figure}

@@

Having chosen values of $D$ equal to the ones obtained for the linear density case, we
are free to explore the integration error as a function of $\delta$ in more detail and
how it varies for different values of $b$ (Eq.~\ref{eq:density-exp}).
Now we perform the error calculations for the every grid detailed in
Table~\ref{tab:grids} for the 20 spherical shells models detailed in
Table~\ref{tab:tess-collections}.
The calculations are repeated for different values of $b$ to examine the error variation
with the sharpness of the density function.
Because larger $\delta$ values result in fewer tesseroid divisions,
our intention is to find the highest value of $\delta$ whose numerical error is bellow
the $0.1\%$ threshold.
